---
title: "Read Me"
output:
  pdf_document: default
  html_notebook: default
  html_document: default
---
```{r include=FALSE, cache = FALSE}
library(tidyverse)
library(ggthemes)
source('svi_h.R')
```

Quasi-explicit calibration of the modified SVI model. The optimization method follows Martini & Marco (2009), with some modificiation. 

The modified SVI function is:

$$ v(x) = [a + b(\rho(x-m)+\sqrt{(x-m)^2 + \sigma^2})]^H
$$

Given that the function has 6 parameters, and many local minimums, two-step quasi-explicit calibration method has some  advantages to find global optimal parameters. 

Read a sample chain (iv.csv, $\tau = 0.12$ ), and fit with the two-step optimization.

```{r, direct, results='asis'}
raw_data <- read_csv("../static/input/IV_Raw_Delta_surface.csv",
                     col_types = cols(date = col_date(format = "%m/%d/%Y")))

slice_data <- raw_data %>% 
  filter(period == 30) %>% 
  mutate(tau = period / 365) %>% 
  select(moneyness, iv, tau)

results <- fit_direct_svi(slice_data$moneyness, 
                          slice_data$iv, 
                          slice_data$tau)
vec <- results %>% 
  select(par, sumse) %>% 
  unlist()
names(vec) <- c("a", "b", "rho", "m", "sigma", "SUMSE")
knitr::kable(as.data.frame(vec))
```

Let's compare this parameterization with real data.

```{r direct_plot}
par <- results$par[[1]]
vol_fit <- tibble(vol_fit = 
                    sqrt(svi_fun(par, slice_data$moneyness) / slice_data$tau))
df <- bind_cols(slice_data, vol_fit)

ggplot(df, aes(x = moneyness, y = iv)) + 
  geom_point() +
  geom_line(aes(y = vol_fit)) +
  # guides(color = guide_legend()) +
  labs(title = "",
       x = "Forward log-moneyness",
       y = "Volatility",
       caption = "") +
  scale_y_continuous(labels = scales::percent) +
  scale_color_viridis_d() +
  theme_economist_white()
```

```{r ga}
# measure estimation time
ptm <- proc.time()
param_ga <- fit_ga_svi(c$k,c$iv,tau)
#show how long it takes for estimate the parameters
print(proc.time()-ptm)
```

```{r, NM}
ptm <- proc.time()
param <- fit_svih(c$k,c$iv,tau, 0.95)
#show how long it takes for estimate the parameters
print(proc.time()-ptm)

print(param)
# SVI parameterized IV estimation
c$svi <- svi_fun(c$k,as.numeric(param[1,2:7]))/sqrt(tau)

# plot fitting results
ggplot(c, aes(x = k, y = iv)) + geom_point()  + 
  geom_line(aes(y = svi), color = 'red')
```

```{r}
c$err = c$iv - c$svi

ggplot(c, aes(x = k, y = err)) + geom_point()
print(sd(c$err))
```
Using `par_fit_svi` function, one can fit the whole surface with paralell computation. An example is shown below:
```{r}
# read a chain
library(parallel)
c2 <- read.csv('chain.csv')
# suppose now H = 0.65. This can be done by using genetic algo
ptm <- proc.time()
para <- par_fit_svi(c2, 0.65)
print(proc.time()-ptm)

print(para)
```


